The role of cognateness in native spoken word recognition

### 2024-10-18 manuscript/manuscript.tex
Fix preprint

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage[]{Times}
\ifPDFTeX\else  
    % xetex/luatex font selection
    \setmainfont[]{Latin Modern Roman}
  \setmathfont[]{Latin Modern Math}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother

@@

\usepackage{booktabs}
\usepackage{caption}
\usepackage{longtable}
\usepackage{colortbl}
\usepackage{array}
\usepackage{float}
\usepackage{tabularray}
\usepackage[normalem]{ulem}
\usepackage{graphicx}
\UseTblrLibrary{booktabs}
\UseTblrLibrary{rotating}
\UseTblrLibrary{siunitx}
\NewTableCommand{\tinytableDefineColor}[3]{\definecolor{#1}{#2}{#3}}
\newcommand{\tinytableTabularrayUnderline}[1]{\underline{#1}}
\newcommand{\tinytableTabularrayStrikeout}[1]{\sout{#1}}
\usepackage{tipa}
\usepackage{booktabs}
\DeclareTextFontCommand\textphonetic{\ipafont}
\usepackage[utf8]{inputenc}
\usepackage{CJKutf8}
\usepackage{arxiv}
\usepackage{orcidlink}
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

@@

\usepackage{lineno}
\linenumbers
\newcommand{\runninghead}{A Preprint }
\renewcommand{\runninghead}{Cognateness and recognition of foreign
words }
\title{The role of cognateness in native spoken word recognition}
\author{\textbf{Gonzalo
Garcia-Castro}~\orcidlink{0000-0002-8553-4209}\\Center for Brain and
Cognition\\Universitat Pompeu Fabra\\Barcelona,
08005\\\texttt{\href{mailto:gonzalo.garciadecastro@upf.edu}{gonzalo.garciadecastro@upf.edu}}\And\textbf{Serene
Siow}~\orcidlink{0000-0001-6482-2191}\\Department of Experimental
Psychology\\University of Oxford\\Oxford, OX2
6GG\\\texttt{\href{mailto:siow.serene@gmail.com}{siow.serene@gmail.com}}\And\textbf{Kim
Plunkett}~\orcidlink{0000-0003-0216-7480}\\Department of Experimental
Psychology\\University of Oxford\\Oxford, OX2
6GG\\\texttt{\href{mailto:kim.plunkett@psy.ox.ac.uk}{kim.plunkett@psy.ox.ac.uk}}\And\textbf{Nuria
Sebastian-Galles}~\orcidlink{0000-0001-6938-2498}\\Center for Brain and
Cognition\\Universitat Pompeu Fabra\\Barcelona,
08005\\\texttt{\href{mailto:nuria.sebastian@upf.edu}{nuria.sebastian@upf.edu}}}
\date{}
\begin{document}
\maketitle
{\bfseries \emph Keywords}
\def\sep{\textbullet\ }
cognate \sep spoken word
recognition \sep phonology \sep bilingualism \sep non-native speech
processing \sep 
lexical access

@@

We created two lists of input words to be presented to participants in
the auditory modality: one in Catalan and one in Spanish. Words in the
Catalan list were 5.02 phonemes long on average (\emph{SD} = 1.49, Range
= 2-8), and the orthographic forms of their English translations (which
participants had to type) were 5.12 characters long on average
(\emph{SD} = 1.56, Range = 3-9). Words in the Spanish list were 5.52
phonemes long on average (\emph{SD} = 1.47, Range = 3-9), and the
orthographic form of their English translations were 5.29 characters
long on average (\emph{SD} = 1.77, Range = 3-12).

@@

\centering
\begin{tblr}[         %% tabularray outer open
]                     %% tabularray outer close
{                     %% tabularray inner open
colspec={Q[]Q[]Q[]Q[]},
cell{2}{1}={c=4}{},cell{8}{1}={c=4}{},cell{25}{1}={c=4}{},
cell{3}{1}={preto={\hspace{1em}}},
cell{4}{1}={preto={\hspace{1em}}},
cell{5}{1}={preto={\hspace{1em}}},
cell{6}{1}={preto={\hspace{1em}}},
cell{7}{1}={preto={\hspace{1em}}},
cell{9}{1}={preto={\hspace{1em}}},
cell{10}{1}={preto={\hspace{1em}}},
cell{11}{1}={preto={\hspace{1em}}},
cell{12}{1}={preto={\hspace{1em}}},
cell{13}{1}={preto={\hspace{1em}}},
cell{14}{1}={preto={\hspace{1em}}},
cell{15}{1}={preto={\hspace{1em}}},
cell{16}{1}={preto={\hspace{1em}}},
cell{17}{1}={preto={\hspace{1em}}},
cell{18}{1}={preto={\hspace{1em}}},
cell{19}{1}={preto={\hspace{1em}}},
cell{20}{1}={preto={\hspace{1em}}},
cell{21}{1}={preto={\hspace{1em}}},
cell{22}{1}={preto={\hspace{1em}}},
cell{23}{1}={preto={\hspace{1em}}},
cell{24}{1}={preto={\hspace{1em}}},
cell{26}{1}={preto={\hspace{1em}}},
cell{27}{1}={preto={\hspace{1em}}},
cell{28}{1}={preto={\hspace{1em}}},
cell{29}{1}={preto={\hspace{1em}}},
cell{30}{1}={preto={\hspace{1em}}},
cell{31}{1}={preto={\hspace{1em}}},
row{1}={,cmd=\bfseries,},
hline{1,2}={1,2,3,4}{solid, 0.1em, black},
row{2}={,cmd=\bfseries,},
hline{3}={1,2,3,4}{solid, 0.1em, black},
row{8}={,cmd=\bfseries,},
hline{8,9}={1,2,3,4}{solid, 0.1em, black},
row{25}={,cmd=\bfseries,},
hline{25,26}={1,2,3,4}{solid, 0.1em, black},
}                     %% tabularray inner close
\toprule
Translation & X-SAMPA & Accuracy (\%) & SE \\ \midrule %% TinyTableHeader
Experiment 1 (cat-ENG) &&& \\
cavall - horse       & /k5BaL/ - /hOs/          & 17.14 & 6.37 \\
llibre - book        & /LiB45/ - /bUk/          & 17.14 & 6.37 \\
camisa - shirt       & /k5miz5/ - /S36t/        & 16.67 & 6.21 \\
poma - apple         & /poma/ - /1pl/           & 16.67 & 6.21 \\
cama - leg           & /kam5/ - /lEg/           & 11.11 & 5.24 \\
Experiment 2 (spa-ENG) &&& \\
pantalon - trousers  & /pantalon/ - /tr0aUs56z/ & 77.42 & 7.51 \\
naranja - orange     & /na4aNxa/ - /Or0I0ndZ/   & 41.94 & 8.86 \\
leche - milk         & /letSe/ - /mIlk/         & 35.48 & 8.59 \\
toro - bull          & /to4o/ - /bUl/           & 33.33 & 8.61 \\
libro - book         & /liB4o/ - /bUk/          & 30.00 & 8.37 \\
cebra - zebra        & /TeB4a/ - /zibr05/       & 29.03 & 8.15 \\
pan - bread          & /pan/ - /br0Ed/          & 29.03 & 8.15 \\
pollo - chicken      & /poLo/ - /tSIkIn/        & 26.67 & 8.07 \\
jirafa - giraffe     & /xi4afa/ - /dZI0r01f/    & 20.69 & 7.52 \\
perro - dog          & /pErro/ - /dAg/          & 16.13 & 6.61 \\
pluma - feather      & /pluma/ - /fED56/        & 16.13 & 6.61 \\
puerta - door        & /pwE4ta/ - /dor/         & 16.13 & 6.61 \\
pie - foot           & /pje/ - /fUt/            & 12.90 & 6.02 \\
caballo - horse      & /kaBaLo/ - /hors/        & 10.34 & 5.66 \\
bocadillo - sandwich & /bokaDiLo/ - /s1ndwItS/  & 10.00 & 5.48 \\
globo - balloon      & /gloBo/ - /b5lun/        & 10.00 & 5.48 \\
Experiment 3 (cat-SPA) &&& \\
fulla - hoja         & /fuL5/ - /oxa/           & 30.43 & 9.59 \\
ull - ojo            & /uL/ - /oxo/             & 21.74 & 8.60 \\
got - vaso           & /gOt/ - /baso/           & 20.00 & 8.00 \\
entrepa - bocadillo  & /ent45pa/ - /bokaDiLo/   & 13.04 & 7.02 \\
mirall - espejo      & /mi4aL/ - /espexo/       & 12.50 & 6.75 \\
\bottomrule
\end{tblr}

>>>>

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
    \setmainfont[]{Latin Modern Roman}
  \setmathfont[]{Latin Modern Math}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother

@@

\usepackage{booktabs}
\usepackage{caption}
\usepackage{longtable}
\usepackage{colortbl}
\usepackage{array}
\usepackage{float}
\usepackage{tabularray}
\usepackage[normalem]{ulem}
\usepackage{graphicx}
\UseTblrLibrary{booktabs}
\UseTblrLibrary{rotating}
\UseTblrLibrary{siunitx}
\NewTableCommand{\tinytableDefineColor}[3]{\definecolor{#1}{#2}{#3}}
\newcommand{\tinytableTabularrayUnderline}[1]{\underline{#1}}
\newcommand{\tinytableTabularrayStrikeout}[1]{\sout{#1}}
\usepackage{tipa}
\usepackage{booktabs}
\usepackage{arxiv}
\usepackage{orcidlink}
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

@@

\usepackage{lineno}
\linenumbers
\newcommand{\runninghead}{A Preprint }
\renewcommand{\runninghead}{Cognateness and recognition of foreign
words }
\title{The role of cognateness in native spoken word recognition}
\def\asep{\\\\\\ } % default: all authors on same column
\def\asep{\And }
\author{\textbf{Gonzalo
Garcia-Castro}~\orcidlink{0000-0002-8553-4209}\\Center for Brain and
Cognition\\Universitat Pompeu Fabra\\Barcelona,
08005\\\href{mailto:gonzalo.garciadecastro@upf.edu}{gonzalo.garciadecastro@upf.edu}\asep\textbf{Serene
Siow}~\orcidlink{0000-0001-6482-2191}\\Department of Experimental
Psychology\\University of Oxford\\Oxford, OX2
6GG\\\href{mailto:siow.serene@gmail.com}{siow.serene@gmail.com}\asep\textbf{Kim
Plunkett}~\orcidlink{0000-0003-0216-7480}\\Department of Experimental
Psychology\\University of Oxford\\Oxford, OX2
6GG\\\href{mailto:kim.plunkett@psy.ox.ac.uk}{kim.plunkett@psy.ox.ac.uk}\asep\textbf{Nuria
Sebastian-Galles}~\orcidlink{0000-0001-6938-2498}\\Center for Brain and
Cognition\\Universitat Pompeu Fabra\\Barcelona,
08005\\\href{mailto:nuria.sebastian@upf.edu}{nuria.sebastian@upf.edu}}
\date{}
\begin{document}
\maketitle
\begin{abstract}
Insert abstract here.
\end{abstract}
{\bfseries \emph Keywords}
\def\sep{\textbullet\ }
cognate \sep spoken word
recognition \sep phonology \sep bilingualism \sep non-native speech
processing \sep 
lexical access

@@

We created two lists of input words to be presented to participants in
the auditory modality: one in Catalan and one in Spanish. Words in the
Catalan list were 6.67 phonemes long on average (\emph{SD} = 2.06, Range
= 2-11), and the orthographic forms of their English translations (which
participants had to type) were 5.12 characters long on average
(\emph{SD} = 1.56, Range = 3-9). Words in the Spanish list were 7.27
phonemes long on average (\emph{SD} = 2.05, Range = 3-13), and the
orthographic form of their English translations were 5.29 characters
long on average (\emph{SD} = 1.77, Range = 3-12).

@@

\centering
\begin{tblr}[         %% tabularray outer open
]                     %% tabularray outer close
{                     %% tabularray inner open
colspec={Q[]Q[]Q[]Q[]},
cell{2}{1}={c=4}{},cell{8}{1}={c=4}{},cell{25}{1}={c=4}{},
cell{3}{1}={preto={\hspace{1em}}},
cell{4}{1}={preto={\hspace{1em}}},
cell{5}{1}={preto={\hspace{1em}}},
cell{6}{1}={preto={\hspace{1em}}},
cell{7}{1}={preto={\hspace{1em}}},
cell{9}{1}={preto={\hspace{1em}}},
cell{10}{1}={preto={\hspace{1em}}},
cell{11}{1}={preto={\hspace{1em}}},
cell{12}{1}={preto={\hspace{1em}}},
cell{13}{1}={preto={\hspace{1em}}},
cell{14}{1}={preto={\hspace{1em}}},
cell{15}{1}={preto={\hspace{1em}}},
cell{16}{1}={preto={\hspace{1em}}},
cell{17}{1}={preto={\hspace{1em}}},
cell{18}{1}={preto={\hspace{1em}}},
cell{19}{1}={preto={\hspace{1em}}},
cell{20}{1}={preto={\hspace{1em}}},
cell{21}{1}={preto={\hspace{1em}}},
cell{22}{1}={preto={\hspace{1em}}},
cell{23}{1}={preto={\hspace{1em}}},
cell{24}{1}={preto={\hspace{1em}}},
cell{26}{1}={preto={\hspace{1em}}},
cell{27}{1}={preto={\hspace{1em}}},
cell{28}{1}={preto={\hspace{1em}}},
cell{29}{1}={preto={\hspace{1em}}},
cell{30}{1}={preto={\hspace{1em}}},
cell{31}{1}={preto={\hspace{1em}}},
row{1}={,cmd=\bfseries,},
hline{1,2}={1,2,3,4}{solid, 0.1em, black},
row{2}={,cmd=\bfseries,},
hline{3}={1,2,3,4}{solid, 0.1em, black},
row{8}={,cmd=\bfseries,},
hline{8,9}={1,2,3,4}{solid, 0.1em, black},
row{25}={,cmd=\bfseries,},
hline{25,26}={1,2,3,4}{solid, 0.1em, black},
}                     %% tabularray inner close
\toprule
Translation & IPA & Accuracy (\%) & SE \\ \midrule %% TinyTableHeader
Experiment 1 (cat-ENG) &&& \\
cavall - horse       & \textipa{/k@'ba}\textlambda\textipa{/ - /hO:s/}                                  & 17.14 & 6.37 \\
llibre - book        & \textipa{/"}\textlambda\textipa{i.BR@/ - /bUk/}                                  & 17.14 & 6.37 \\
camisa - shirt       & \textipa{/ka.'mi.za/ - /S3:t/}                                                     & 16.67 & 6.21 \\
poma - apple         & \textipa{/"po.ma/ - /"aepl/}                                                       & 16.67 & 6.21 \\
cama - leg           & \textipa{/"ka.m@/ - /lEg/}                                                         & 11.11 & 5.24 \\
Experiment 2 (spa-ENG) &&& \\
pantalon - trousers  & \textipa{/paN.ta"lon/ - /"traUz@z/}                                                & 77.42 & 7.51 \\
naranja - orange     & \textipa{/na"RaN.xa/ - /"6rIn}\textdyoghlig\textipa{/}                           & 41.94 & 8.86 \\
leche - milk         & \textipa{/"le.}\textteshlig\textipa{e/ - /mIlk/}                                 & 35.48 & 8.59 \\
toro - bull          & \textipa{/"to.Ro/ - /bUl/}                                                         & 33.33 & 8.61 \\
libro - book         & \textipa{/"li.BRo/ - /bUk/}                                                        & 30.00 & 8.37 \\
cebra - zebra        & \textipa{/"Te.bRa/ - /"zi:br@/}                                                    & 29.03 & 8.15 \\
pan - bread          & \textipa{/pan/ - /brEd/}                                                           & 29.03 & 8.15 \\
pollo - chicken      & \textipa{/"po.}\textlambda\textipa{o/ - /"}\textteshlig\textipa{IkIn/}         & 26.67 & 8.07 \\
jirafa - giraffe     & \textipa{/xi'Ra.fa/ - /}\textdyoghlig\textipa{I"rA:f/}                           & 20.69 & 7.52 \\
perro - dog          & \textipa{/pe.ro/ - /d6g/}                                                          & 16.13 & 6.61 \\
pluma - feather      & \textipa{/plu.ma/ - /"fED@/}                                                       & 16.13 & 6.61 \\
puerta - door        & \textipa{/pwer.ta/ - /dO:/}                                                        & 16.13 & 6.61 \\
pie - foot           & \textipa{/pje/ - /fUt/}                                                            & 12.90 & 6.02 \\
caballo - horse      & \textipa{/ka"Ba.}\textlambda\textipa{o/ - /hO:s/}                                & 10.34 & 5.66 \\
bocadillo - sandwich & \textipa{/bo.ka"di.}\textlambda\textipa{o/ - /"saenwI}\textdyoghlig\textipa{/} & 10.00 & 5.48 \\
globo - balloon      & \textipa{/"glo.Bo/ - /b@"lu:n/}                                                    & 10.00 & 5.48 \\
Experiment 3 (cat-SPA) &&& \\
fulla - hoja         & \textipa{/"fu.}\textlambda\textipa{@/ - /"o.xa/}                                 & 30.43 & 9.59 \\
ull - ojo            & \textipa{/u}\textlambda\textipa{/ - /"o.xo/}                                     & 21.74 & 8.60 \\
got - vaso           & \textipa{/"gOt/ - /"ba.so/}                                                        & 20.00 & 8.00 \\
entrepa - bocadillo  & \textipa{/ˌen.tR@"pa/ - /bo.ka"di.}\textlambda\textipa{o/}                       & 13.04 & 7.02 \\
mirall - espejo      & \textipa{/mi"Ra}\textlambda\textipa{/ - /es'pe.xo/}                              & 12.50 & 6.75 \\
\bottomrule
\end{tblr}
